```
title: "project"
author: "Karthik Kurella (17MIS1022)"
date: "25/08/2020"
```

```{r,echo=FALSE}
#install.packages("mltools")
library(tidyverse)
library(forcats)
library(ggplot2)
library(dplyr)
library(stargazer)
library(caret)
library(modelr)
library(Hmisc)
library(DataExplorer)
library(usmap)
library(ggplot2)
library(skimr)
library(devtools)
library(visdat)
library(tidyr)
library(tidyverse)
library(forcats)
library(readr)
library(dplyr)
library(arules)
library(mltools)
library(arulesViz)
library(factoextra)
library(stats)
library(klaR)
library(e1071)


library(rpart)
library(rattle)
library(rpart.plot)
library(RColorBrewer)
library(class) 
library(gmodels)
library(ggplot2)

library(MASS)
library(FactoMineR)
```

```{r}
ACSData<- read_csv("E:\\Sems\\sem-7\\Intro to Data Analytics\\proj_data\\ACS_full_data_wo_over_60.csv")
```

```{r}
nrow(ACSData)
#str(ACSData)
ncol(ACSData)
colnames(ACSData)
```

```{r}
head(ACSData)
```

DataCleaning

```{r}
ACSData$X1<-factor(ACSData$X1)
ACSData$STATE<-factor(ACSData$STATE)
ACSData$COUNTY<-factor(ACSData$COUNTY)
```

```{r}
plot_str(ACSData)
```

```{r}
plot_intro(ACSData)
```

```{r}
#Checking for any NA values
sum(is.na(ACSData))
library(DataExplorer)
plot_missing(ACSData[,1:33])
plot_missing(ACSData[,34:66])
plot_missing(ACSData[,67:99])
plot_missing(ACSData[,100:133])

```

```{r}
introduce(ACSData)
```

```{r}
CountByState = ACSData[,c(2,5,6,7,8,132,133)]
head(CountByState)
#str(CountByState)

CountByState_agg = aggregate(CountByState[,c(2,3,4,5,6,7)],
                by = list(ACSData$STATE),
                FUN = sum)

names(CountByState_agg)[names(CountByState_agg) == "Group.1"] <- "state"

head(CountByState_agg)
```

```{r}
CountByState_agg$'Confirmed_Increased_Perc' <- ((CountByState_agg$'4_22_Confirmed' - CountByState_agg$'4_16_Confirmed') / CountByState_agg$'4_16_Confirmed') * 100

CountByState_agg$'Deaths_Increased_Perc' <- ((CountByState_agg$'4_22_Deaths' - CountByState_agg$'4_16_Deaths') / CountByState_agg$'4_16_Deaths') * 100

CountByState_agg$'Confirmed_Increased_Perc' <- round(CountByState_agg$'Confirmed_Increased_Perc', 2)

CountByState_agg$'Deaths_Increased_Perc' <- round(CountByState_agg$'Deaths_Increased_Perc', 2)

head(CountByState_agg)
```

```{r}
# create groups

CountByState_agg_0422C = CountByState_agg[,c(1,2)]
head(CountByState_agg_0422C)

CountByState_agg_0422D= CountByState_agg[,c(1,3)]
head(CountByState_agg_0422D)

CountByState_agg_0416C= CountByState_agg[,c(1,4)]
head(CountByState_agg_0416C)

CountByState_agg_0416D= CountByState_agg[,c(1,5)]
head(CountByState_agg_0416D)

CountByState_agg_DeathRise= CountByState_agg[,c(1,6)]
head(CountByState_agg_DeathRise)

CountByState_agg_ConfirmedRise= CountByState_agg[,c(1,7)]
head(CountByState_agg_ConfirmedRise)
```

```{r}
#order from high to low with '4_22_Confirmed'
CountByState_agg_0422C[order(-CountByState_agg$'4_22_Confirmed'),]
#order from high to low with '4_22_Deaths'
CountByState_agg_0422D[order(-CountByState_agg$'4_22_Deaths'),]
#order from high to low with '4_16_Confirmed'
CountByState_agg_0416C[order(-CountByState_agg$'4_16_Confirmed'),]
#order from high to low with '4_16_Deaths'
CountByState_agg_0416D[order(-CountByState_agg$'4_16_Deaths'),]
#order from high to low with 'Death_Rise_4_16_to_20'
CountByState_agg_DeathRise[order(-CountByState_agg$'Death_Rise_4_16_to_20'),]
#order from high to low with 'Confirmed_Rise_4_16_to_20'
CountByState_agg_ConfirmedRise[order(-CountByState_agg$'Confirmed_Rise_4_16_to_20'),]
```

```{r}
plot_usmap(data = CountByState_agg_0422C, values = "4_22_Confirmed", color = "red") + 
  scale_fill_continuous(low = "white", high = "red", name = "04/22 COVID-19 Confirmed", label = scales::comma) + 
  theme(legend.position = "right")

plot_usmap(data = CountByState_agg_0422D, values = "4_22_Deaths", color = "red") + 
  scale_fill_continuous(low = "white", high = "red", name = "04/22 COVID-19 Deaths", label = scales::comma) + 
  theme(legend.position = "right")

plot_usmap(data = CountByState_agg_0416C, values = "4_16_Confirmed", color = "red") + 
  scale_fill_continuous(low = "white", high = "red", name = "04/16 COVID-19 Confirmed", label = scales::comma) + 
  theme(legend.position = "right")

plot_usmap(data = CountByState_agg_0416D, values = "4_16_Deaths", color = "red") + 
  scale_fill_continuous(low = "white", high = "red", name = "04/16 COVID-19 Deaths", label = scales::comma) + 
  theme(legend.position = "right")

plot_usmap(data = CountByState_agg_DeathRise, values = "Death_Rise_4_16_to_20", color = "red") + 
  scale_fill_continuous(low = "white", high = "red", name = "COVID-19 Deaths Increased\nfrom 04/16 to 04/22", label = scales::comma) + 
  theme(legend.position = "right")

plot_usmap(data = CountByState_agg_ConfirmedRise, values = "Confirmed_Rise_4_16_to_20", color = "red") + 
  scale_fill_continuous(low = "white", high = "red", name = "COVID-19 Confirmed Increased\nfrom 04/16 to 04/22", label = scales::comma) + 
  theme(legend.position = "right")
```

```{r}
str(CountByState_agg)
#Barplot 4_22_Confirmed
par(mar=c(11,4,2,4))
barplot(CountByState_agg$'4_22_Confirmed',
main = "Infected with COVID-19 0422 Confirmed",
names = CountByState_agg$STATE,
col = "darkred",
las=2,
horiz = FALSE)

#Barplot 4_22_Deaths
barplot(CountByState_agg$'4_22_Deaths',
main = "Infected with COVID-19 0422 Deaths",
names = CountByState_agg$STATE,
col = "darkred",
las=2,
horiz = FALSE)

#Barplot 4_16_Confirmed
barplot(CountByState_agg$'4_16_Confirmed',
main = "Infected with COVID-19 0416 Confirmed",
names = CountByState_agg$STATE,
col = "darkred",
las=2,
horiz = FALSE)

#Barplot 4_16_Deaths
barplot(CountByState_agg$'4_16_Deaths',
main = "Infected with COVID-19 0416 Deaths",
names = CountByState_agg$STATE,
col = "darkred",
las=2,
horiz = FALSE)

#Barplot Death_Rise_4_16_to_20
barplot(CountByState_agg$'Death_Rise_4_16_to_20',
main = "Infected with COVID-19 Death Rise 0416 to 0420",
names = CountByState_agg$STATE,
col = "darkred",
las=2,
horiz = FALSE)

#Barplot Confirmed_Rise_4_16_to_20
barplot(CountByState_agg$'Confirmed_Rise_4_16_to_20',
main = "Infected with COVID-19 Confirmed Rise 0416 to 0420",
names = CountByState_agg$STATE,
col = "darkred",
las=2,
horiz = FALSE)
```
```{r}
plot(CountByState_agg$'4_22_Confirmed', CountByState_agg$'4_22_Deaths')
plot(CountByState_agg$'4_16_Confirmed', CountByState_agg$'4_16_Deaths')
plot(CountByState_agg$'Confirmed_Rise_4_16_to_20', CountByState_agg$'Death_Rise_4_16_to_20')
```
```{r}
boxplot(CountByState_agg$'4_22_Confirmed', main="4_22_Confirmed")
boxplot(CountByState_agg$'4_22_Deaths', main="4_22_Deaths")
boxplot(CountByState_agg$'4_16_Confirmed', main="4_16_Confirmed")
boxplot(CountByState_agg$'4_16_Deaths', main="4_16_Deaths")
boxplot(CountByState_agg$'Confirmed_Rise_4_16_to_20', main="Confirmed_Rise_4_16_to_20")
boxplot(CountByState_agg$'Death_Rise_4_16_to_20', main="Death_Rise_4_16_to_20")
```
```{r}
plot(CountByState_agg$'4_22_Confirmed', log(CountByState_agg$'4_22_Confirmed'), main="4_22_Confirmed")
plot(CountByState_agg$'4_22_Deaths', log(CountByState_agg$'4_22_Deaths'), main="4_22_Deaths")
plot(CountByState_agg$'4_16_Confirmed', log(CountByState_agg$'4_16_Confirmed'), main="4_16_Confirmed")
plot(CountByState_agg$'4_16_Deaths', log(CountByState_agg$'4_16_Deaths'), main="4_16_Deaths")
plot(CountByState_agg$'Confirmed_Rise_4_16_to_20', log(CountByState_agg$'Confirmed_Rise_4_16_to_20'), main="Confirmed_Rise_4_16_to_20")
plot(CountByState_agg$'Death_Rise_4_16_to_20', log(CountByState_agg$'Death_Rise_4_16_to_20'), main="Death_Rise_4_16_to_20")
```
```{r}
AggregateByState = ACSData[,2:133]
AggregateByState = AggregateByState[,-2]
head(AggregateByState)
ncol(AggregateByState)
AggregateByState %>% drop_na()
```
```

```{r}
AggregateByState = ACSData[,2:133]
AggregateByState = AggregateByState[,-2]
AggregateByState %>% drop_na()
head(AggregateByState)
#str(AggregateByState)

AggregateByState_all = aggregate(AggregateByState[,2:131],
                by = list(AggregateByState$STATE),
                FUN = sum)

#AggregateByState_all
names(AggregateByState_all)
names(AggregateByState_all)[names(AggregateByState_all) == "Group.1"] <- "state"
head(AggregateByState_all)
```

Preprocess the Data

```{r}
D <- data.frame (ACSData)
#str(D)
#colnames(D)
Original_D_Col <- ncol(D)
```

```{r}
D$Confirmed_Per_Capita_4_22 <- D$X4_22_Confirmed / D$ET_Total_Population
D$Deaths_Per_Capita_4_22    <- D$X4_22_Deaths    / D$ET_Total_Population
D$Deaths_Per_Confirmed_4_22 <- D$Deaths_Per_Capita_4_22 / D$Confirmed_Per_Capita_4_22

D$Confirmed_Per_Capita_4_16 <- D$X4_16_Confirmed / D$ET_Total_Population
D$Deaths_Per_Capita_4_16    <- D$X4_16_Deaths    / D$ET_Total_Population
D$Deaths_Per_Confirmed_4_16 <- D$Deaths_Per_Capita_4_16 / D$Confirmed_Per_Capita_4_16 


D$Two_Week_Confirm_Rate_Per_Capita <- (D$X4_22_Confirmed-D$X4_16_Confirmed)/D$ET_Total_Population
D$Two_Week_Death_Rate_Per_Capita <- (D$X4_22_Death-D$X4_16_Death)/D$ET_Total_Population

D$Fraction_Female <- D$E_Total_Pop_SEX_Female / D$ET_Total_Population

D$Fraction_White <- D$E_Total_Pop_RACE_White / D$ET_Total_Population
D$Fraction_Black <- D$E_Total_Pop_RACE_Black / D$ET_Total_Population
D$Fraction_Other <- (D$E_Total_Pop_RACE_Native_Pop + D$E_Total_Pop_RACE_Asian +
                     D$E_Total_Pop_RACE_Pacific_Islander + D$E_Total_Pop_RACE_Other_Race +
                     D$E_Total_Pop_RACE_Two_or_More_Races) / D$ET_Total_Population

D$Hispanic <- D$E_Total_Pop_RACE_Hispanic / D$ET_Total_Population

D$Population_Over_Age_15 <- D$E_Total_Pop_Over_15_EDUCATION_Less_Than_High_School + 
                          D$E_Total_Pop_Over_15_EDUCATION_High_School_Grad + 
                          D$E_Total_Pop_Over_15_EDUCATION_Some_College+ 
                          D$E_Total_Pop_Over_15_EDUCATION_Bachelors_Degree_or_Higher
D$Fraction_Less_Than_HS <-        D$E_Total_Pop_Over_15_EDUCATION_Less_Than_High_School / D$Population_Over_Age_15
D$Fraction_High_School_Grad <-    D$E_Total_Pop_Over_15_EDUCATION_High_School_Grad / D$Population_Over_Age_15
D$Fraction_Some_College <-        D$E_Total_Pop_Over_15_EDUCATION_Some_College / D$Population_Over_Age_15
D$Fraction_Bachelors_or_Higher <- D$E_Total_Pop_Over_15_EDUCATION_Bachelors_Degree_or_Higher / D$Population_Over_Age_15

D$Fraction_Disabled <- D$E_Total_Pop_DISABILITY_STATUS_Yes / D$ET_Total_Population

D$Fraction__Limited_English <- D$E_Total_Pop_Over_5_LANGUAGE_Limited_English / D$ET_Total_Population

D$Fraction_Unemployed <- D$E_Total_Pop_Over_16_EMPLOYMENT_STATUS_In_Civilian_Labor_Force_Unemployed / 
                         D$ET_Total_Pop_Over_16_EMPLOYMENT_STATUS_In_Labor_Force

D$Fraction_Below_Poverty_Line <- D$E_Total_Pop_POVERTY_STATUS_Below_100_Percent / D$ET_Total_Population
D$Fraction_Btwn_100_149_Above_Poverty_Line <- D$E_Total_Pop_POVERTY_STATUS_Btwn_100_149_Percent / D$ET_Total_Population
D$Fraction_Not_Citizen <- D$E_Total_Pop_CITIZENSHIP_Foreign_Born_Not_US_Citizen / D$ET_Total_Population
```

```{r}
E<- D[,1:10]
#str(E)
cnames <- colnames(E)
cnames[1] <- c("ID")
cnames[5] <- c("Confirmed_4_22")
cnames[6] <- c("Deaths_4_22")
cnames[7] <- c("Confirmed_4_16")
cnames[8] <- c("Deaths_4_16")
cnames
colnames(E) <- cnames
```

```{r}

Original_D_Col
New_D_Col <- ncol(D)
New_D_Col
D_Col_to_Add <- Original_D_Col+1

E <- data.frame(E,D[,D_Col_to_Add:New_D_Col])
colnames(E)
ncol(E)
#head(E)
#str(E)
```

```{r}
E$Confirmed_4_16 <- as.numeric(E$Confirmed_4_16)
E$Deaths_4_16 <- as.numeric(E$Deaths_4_16)
E$Confirmed_4_22 <- as.numeric(E$Confirmed_4_22)
E$Deaths_4_22 <- as.numeric(E$Deaths_4_22)
E$ET_Total_Population <- as.numeric(E$ET_Total_Population)
```

```{r}
New_Data <- data.frame(E)
#str(New_Data)
# Look for any NAs
sum(is.na(New_Data))

New_Data <- na.omit(New_Data)
sum(is.na(New_Data))
```
```{r}
summary(New_Data)
summary(New_Data$Deaths_Per_Confirmed_4_16)

```

```{r}
g <- ggplot(New_Data, aes(x=Confirmed_4_16, y=Deaths_Per_Confirmed_4_16))
g <- g+ geom_point(shape=1) + ggtitle("Scatter Plot of Normalized Death Rates vs Confirmed Cases")
g
```

```{r}
DataZoomed<- New_Data[New_Data$Confirmed_4_16<100,]

nrow(DataZoomed)
g <- ggplot(DataZoomed, aes(x=Confirmed_4_16, y=Deaths_Per_Confirmed_4_16))
g <- g+ geom_point(shape=1) + ggtitle("Scatter Plot of Normalized Death Rates vs Confirmed Cases Zoomed into Comfirmed<100")
g
```

```{r}
BigRatesRow <- which(New_Data$Deaths_Per_Confirmed_4_16>.25)
BigRatesRow
```

```{r}
BigRatesZScore <- (New_Data$Deaths_Per_Confirmed_4_16[BigRatesRow]-mean(New_Data$Deaths_Per_Confirmed_4_16[]))/
  sd(New_Data$Deaths_Per_Confirmed_4_16)
BigRatesZScore 
```

```{r}
Threshold <- 3*sd(New_Data$Deaths_Per_Confirmed_4_16) +mean(New_Data$Deaths_Per_Confirmed_4_16)
Threshold
```

```{r}
BigRatesRow <- which(New_Data$Deaths_Per_Confirmed_4_16>Threshold)
BigRatesRow
New_Data$Confirmed_4_16[BigRatesRow]
```

```{r}
No_Outliers <- New_Data[New_Data$Deaths_Per_Confirmed_4_16<Threshold,]
nrow(New_Data)
nrow(No_Outliers)
```

```{r}

g <- ggplot(No_Outliers, aes(x=Confirmed_4_16, y=Deaths_Per_Confirmed_4_16))
g <- g+ geom_point(shape=1) + ggtitle("Scatter Plot of Normalized Death Rates vs Confirmed Cases w/ Outliers Removed")
g

```

```{r}
#str(No_Outliers)
SmallData <- data.frame(No_Outliers[,-c(5,6,7,8,11,12,14,15,17,18)])
glimpse(SmallData)
#str(SmallData)
```

```{r}
Min_Max_function <- function(x) {
  return( (x-min(x)) / (max(x) - min(x)))
}

SmallDataNumeric <- SmallData[,-1:-3]
ncol(SmallDataNumeric)
#str(SmallDataNumeric)
SmallNorm <- as.data.frame(lapply(SmallDataNumeric,Min_Max_function))
#str(SmallNorm)
summary(SmallNorm)
SmallNorm <- SmallNorm[,-4]
ncol(SmallDataNumeric)
```

```{r}
hist(SmallData$Deaths_Per_Confirmed_4_16)
```

```{r}
g <- ggplot(SmallNorm, aes(x=Deaths_Per_Confirmed_4_16))
g <- g+ geom_histogram(binwidth=.025) + ggtitle("Histogram of Normalizes Death Rates Zoomed into binwidth = .025")
g
```

```{r}
g <- ggplot(SmallNorm, aes(x=Deaths_Per_Confirmed_4_16))
g <- g+ geom_histogram(binwidth=.025)  + ggtitle("Histogram of Normalizes Death Rates Zoomed into binwidth = .005")
g

```

```{r}
Preprocessed_Data <- SmallNorm
Preprocessed_Data[, "Deaths_Per_Confirmed_4_16"] <- bin_data(Preprocessed_Data$Deaths_Per_Confirmed_4_16, bins=c(0,0.05,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1.0), binType = "explicit")
counts <- table(Preprocessed_Data$Deaths_Per_Confirmed_4_16)
barplot(counts, main="Count per Bin for Deaths_Per_Confirmed_4_16", 
   xlab="Deaths_Per_Confirmed_4_16",las=3)
```

Classification

```{r}

#SmallNorm
ClassData<- SmallNorm
#str(ClassData)
ClassData$Bin<-Preprocessed_Data$Deaths_Per_Confirmed_4_16
colnames(ClassData)
ClassData <- ClassData[,-4]
colnames(ClassData)
#str(ClassData)
#ncol(ClassData)
```

KNN with Cross Fold Validation

```{r}
#str(training)
data<-ClassData
set.seed(300)
indxTrain <- createDataPartition(y = data$Bin,p = 0.75,list = FALSE)
training <- data[indxTrain,]
testing <- data[-indxTrain,] 
x <- training[,-20]
y <- training$Bin
model <- train(x,y, 'knn',trControl=trainControl(method='cv',number=5), tuneLength=20)
model

Prediction <- predict(model, newdata=testing)
#Results <- table(unlist(Prediction),unlist(testing$Bin))
#Results <-as.data.frame.matrix(Results)
#Results
confusionMatrix(Prediction, testing$Bin)
plot(testing$Bin, ylab="Density",main="Test Data")
plot(  Prediction, ylab = "Density", main = "KNN Plot")
```

* Observation: 25 values of K were attempted. K=53 was best with an training accuracy of 50% and kappa .18 The testing accuracy is 49% This model is putting most of the predictions in the first bin and a few in the 3rd and 4th and none elsewhere

SVM - Linear Kernel 
```{r}
trctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)
set.seed(333)
model <- train(Bin ~., data = training, method = "svmLinear",
                 trControl=trctrl,
                 preProcess = c("center", "scale"),
                 tuneLength = 10)
model
Prediction <- predict(model, newdata=testing)
plot(testing$Bin, ylab="Density",main="Test Data")
plot(  Prediction, ylab = "Density", main = "SVM Linear Plot")

# Results <- table(unlist(Prediction),unlist(testing$Bin))
# Results <-as.data.frame.matrix(Results)
# Results
confusionMatrix(Prediction, testing$Bin)
summary(model)
```
```{r}

grid <- expand.grid(C = c(0,0.01, 0.05, 0.1, 0.25, 0.5, 0.75, 1, 1.25, 1.5, 1.75, 2,5))
model <- train(Bin ~., data = training, method = "svmLinear",
                 trControl=trctrl,
                 preProcess = c("center", "scale"),
                 tuneGrid = grid,
                 tuneLength = 10)
model
Prediction <- predict(model, newdata=testing)
plot(testing$Bin, ylab="Density",main="Test Data")
plot(  Prediction, ylab = "Density", main = "SVM Linear tuned Plot")

confusionMatrix(Prediction, testing$Bin)
```
```{r}

MyDF <- SmallDataNumeric[,-4]
dim(MyDF)
 str(MyDF)
Temp <- MyDF[,-4]
#str(Temp)
Temp<-t(Temp)
#class(Temp)
#str(Temp)
#class(Temp)
ncol(Temp)
pca = PCA(Temp)
pca$var$coord

DigitDF = data.frame(MyDF$Deaths_Per_Confirmed_4_16,pca$var$coord)
dim(DigitDF)
head(DigitDF)
#unique(DigitDF$MyDF.label)
cnames <- colnames(DigitDF)
cnames[1]<- c("Deaths_Per_Confirmed_4_16")
colnames(DigitDF)<-cnames
str(DigitDF)


NormDeathRate <- (DigitDF$Deaths_Per_Confirmed_4_16 - min(DigitDF$Deaths_Per_Confirmed_4_16)) /
(max(DigitDF$Deaths_Per_Confirmed_4_16)-min(DigitDF$Deaths_Per_Confirmed_4_16))
 NormDeathRate <- as.data.frame(NormDeathRate)
 str(NormDeathRate)
 summary(NormDeathRate)
 colnames(NormDeathRate)

 NormDeathRate[, "NormDeathRate"] <- bin_data(NormDeathRate$NormDeathRate, bins=c(0,0.05,0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1.0), binType = "explicit")


NormDeathRatePCA <- data.frame(NormDeathRate, DigitDF)

NormDeathRatePCA <- NormDeathRatePCA[,-2]
#summary(NormDeathRatePCA)
cname<- colnames(NormDeathRatePCA)
cname
cname[1]<-c("Bin")
colnames(NormDeathRatePCA)<-cname
str(NormDeathRatePCA)
data<-NormDeathRatePCA
set.seed(300)
indxTrain <- createDataPartition(y = data$Bin,p = 0.75,list = FALSE)
training <- data[indxTrain,]
testing <- data[-indxTrain,] 

prop.table(table(training$Bin)) * 100

prop.table(table(testing$Bin)) * 100


x <- training[,-1]
y <- training$Bin

control <- trainControl(method="repeatedcv", number=10, repeats=3)
seed <- 7
metric <- "Accuracy"
set.seed(seed)
mtry <- sqrt(ncol(x))
tunegrid <- expand.grid(.mtry=mtry)
model <- train(Bin~., data=training, method="rf", metric=metric, tuneGrid=tunegrid, trControl=control)
print(model)
Prediction <- predict(model, newdata=testing)
plot(testing$Bin, ylab="Density",main="Test Data")
plot(  Prediction, ylab = "Density", main = "PCA RF Plot")

# Results <- table(unlist(Prediction),unlist(testing$Bin))
# Results <-as.data.frame.matrix(Results)
# Results
confusionMatrix(Prediction, testing$Bin)

```
* Observation:With a training accuracy of 47% that is performed on the cross validation of 10 fold, repeated 3 times. 
The PCA analysis was able to reduce the dimension from 19 to 5 dimensions . This is fed with the features of DF(Death on 4_16) and then predicted.


N